Plot the density distributions of the IHC and CPE tumour purity estimates across all subtypes:
```{r}
library(colorspace)
library(ggrepel)
library(dplyr)
library(tidyr)
library(lattice)
library(knitr)
library(RColorBrewer)

load("~/Documents/project/datasubtypes_my.Rdata")
load("~/Documents/project/Tumor.purity.L.Rdata")
plot(density(Tumor.purity.L[!is.na(Tumor.purity.L$CPE),]$CPE))
Tumor.purity.Lp <- Tumor.purity.L[,c(1,6,7)] 
TPlong <-Tumor.purity.Lp%>%
  tidyr::gather( "type", "purity_fraction", -Sample.ID)
# compute densities for yields
sub_dens <- group_by(TPlong, type) %>% do(ggplot2:::compute_density(na.omit(.$purity_fraction), NULL)) %>%
  dplyr::rename(purity_fraction = x)

# get the maximum values
sub_max <- filter(sub_dens, density == max(density)) %>%
  ungroup() %>% mutate(hjust = c(1,  -1),  vjust = c(-1.5, 1.0))

brewer.pal<- brewer.pal(n=8, name = 'Set1')
cols<- brewer.pal[c(1,2,3,4,5)]

ggplot(TPlong) + 
  geom_density(aes(x = purity_fraction, color = type, fill=type), alpha=0.2) +
  xlab("Tumour Purity") +

  
  scale_color_manual(values=darken(cols, 0.3),
    guide = "none") +
  
  scale_fill_manual(values=cols,
    guide = "none") +
  theme_minimal() +
  
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title = element_blank())+facet_wrap(~type)
```

Perform statistical analysis of the tumour purity across pairs of subtypes to see if the diffferences between the means and the medians of each pair of subtypes is significant as well as to check the correlation of each for CPE and IHC:
```{r}
stattest<-function(x, y){
  t <- t.test(x, y, alternative = "two.sided", var.equal=F, paired=F)
  w <- wilcox.test(x, y)
  c <- cor.test(x, y)
  output = list("tResults" = t, "wResults" = w, "cResults" = c)
  
  return(output)
}
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Her2"),]$CPE, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Basal"),]$CPE)#not sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumB"),]$CPE, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Basal"),]$CPE)#notsig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumA"),]$CPE, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Her2"),]$CPE)#notsig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumA"),]$CPE, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Basal"),]$CPE)#sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumA"),]$CPE, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumB"),]$CPE)#sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumB"),]$CPE, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Normal"),]$CPE)#sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Her2"),]$CPE, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Normal"),]$CPE)#sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Basal"),]$CPE, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Normal"),]$CPE)#sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumA"),]$CPE, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Normal"),]$CPE)
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumB"),]$CPE, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Her2"),]$CPE)

stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Her2"),]$IHC, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Basal"),]$IHC)#not sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumB"),]$IHC, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Basal"),]$IHC)#notsig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumA"),]$IHC, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Her2"),]$IHC)#notsig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumA"),]$IHC, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Basal"),]$IHC)#sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumA"),]$IHC, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumB"),]$IHC)#sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumB"),]$IHC, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Normal"),]$IHC)#sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Her2"),]$IHC, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Normal"),]$IHC)#sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Basal"),]$IHC, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Normal"),]$IHC)#sig
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumA"),]$IHC, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Normal"),]$IHC)
stattest(datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.LumB"),]$IHC, datasubtypes_my[which(datasubtypes_my$subtype == "BRCA.Her2"),]$IHC)
```

Violin plot of the tumour purity across subtypes:
```{r}
library("ggpubr")
violin<- ggplot(datasubtypes_my1, aes(y = subtype, x = CPE,
          color = subtype)) +  geom_violin() +
  theme_minimal() +
  scale_color_manual(values=darken(cols, 0.3),
    guide = "none") +
  xlab("Tumour Purity (CPE)") +ylab(" ")+
  geom_boxplot(width=0.1)+
  theme(legend.position = "none",
        panel.grid.major.x = element_line(colour="grey", size=0.4),
        panel.grid.minor.y = element_blank(),
        #panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title = element_blank())
ggsave("violin.png")
```

plot density plots on top of each other:
```{r}
dens_datasubtypes_my<- group_by(datasubtypes_my1, subtype) %>% do(ggplot2:::compute_density(na.omit(.$CPE), NULL)) %>%
  dplyr::rename(CPE = x)
dens_datasubtypes_my$subtype <- as.factor(dens_datasubtypes_my$subtype)

# get the maximum values
datasubtypes_my_max <- dplyr::filter(dens_datasubtypes_my, density == max(density)) %>%
  ungroup() %>% mutate(hjust = c(3.0, 1.5, 0.0, -2.0, -4.0),  vjust = c(-1.5, -3.0, 1.0, -1.5, 3.0))
datasubtypes_my_max$names <-  datasubtypes_my_max$subtype
library(RColorBrewer)
brewer.pal<- brewer.pal(n=8, name = 'Set1')
cols<- brewer.pal[c(1,2,3,4,5)]

ggplot(datasubtypes_my1) + 
  geom_density(aes(x = CPE, color = subtype, fill=subtype), alpha=0.2) +
  xlab("Tumour Purity (CPE)") +
  ylab("Density")+
  
  scale_color_manual(values=darken(cols, 0.3),
    guide = "none") +
  
  scale_fill_manual(values=cols,
    guide = "none") +
  theme_minimal() +
  
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title = element_blank())+facet_wrap(~subtype)



ggplot(datasubtypes_my1) + 
  geom_density(aes(x = CPE, color = subtype, fill=subtype), alpha=0.2) +
  xlab("Tumour Purity (CPE)") +
  ylab("Density")+
  geom_text_repel(data = datasubtypes_my_max,aes(  label = names, hjust = hjust, vjust = vjust, color = subtype, x = CPE, y = density),
    inherit.aes = FALSE,
    size = 10/.pt, min.segment.length = unit(0.0, 'lines'), segment.size = 0.2
  ) +
  
  scale_color_manual(values=darken(cols, 0.3),
    guide = "none") +
  
  scale_fill_manual(values=cols,
    guide = "none") +
  theme_minimal() +
  
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title = element_blank())
```





















